An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-12 EconGrowth2.Rnw
Now using 36-panel graph for CES alpha, beta, and gamma.

Figure~\ref{fig:CES_ternary_graph_kl} shows 
$\alpha$, $\beta$, and $\gamma$ parameters from the CES model without energy.

<<CES_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
cesResampleTrianglePlot(energyType=NA)
@

Figure~\ref{fig:CESq_ternary_graph_kle} shows 
$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.

<<CESq_ternary_graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($kl$)$e$ nesting.">>=
cesResampleTrianglePlot(energyType="Q", nest="(kl)e")
@

Figure~\ref{fig:CESq_ternary_graph_lek} shows 
$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.

<<CESq_ternary_graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($le$)$k$ nesting.">>=
cesResampleTrianglePlot(energyType="Q", nest="(le)k")
@

Figure~\ref{fig:CESq_ternary_graph_ekl} shows 
$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.

<<CESq_ternary_graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($ek$)$l$ nesting.">>=
cesResampleTrianglePlot(energyType="Q", nest="(ek)l")
@

>>>>

Figure~\ref{fig:CES_ternary_graph} shows 
$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.

<<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesResampleTrianglePlot(energyType="Q", nest="all")
@
